---
title: Leaflet and Plotly Widgets Showcase
author: Carl Howe
date: '2019-08-06'
slug: Leaflet and Plotly demo
categories: []
tags: []
subtitle: ''
summary: ''
authors: []
lastmod: '2019-08-06T10:50:03-04:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
projects: []
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
```

### Leaflet is a JavaScript library for creating dynamic maps that support panning and zooming along with various annotations.

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tibble)
library(leaflet)
locations <- tibble(lng = c(-71.038169, -71.071856),
                    lat = c(42.3488172, 42.349110),
                    label = c("RStudio HQ", "Liberty Mutual"))
leaflet() %>%
  addTiles() %>%
  addMarkers(lng=locations$lng, lat=locations$lat, popup=locations$label) 
```

***

https://rstudio.github.io/leaflet/

- Interactive panning/zooming

- Compose maps using arbitrary combinations of map tiles, markers, polygons, lines, popups, and GeoJSON.

- Create maps right from the R console or RStudio

- Embed maps in knitr/R Markdown documents and Shiny apps

- Easily render Spatial objects from the sp package, or data frames with latitude/longitude columns

- Use map bounds and mouse events to drive Shiny logic




### Plotly provides bindings to the plotly.js library and allows you to easily translate your ggplot2 graphics into an interactive web-based version.

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(plotly)
p <- ggplot(data = diamonds, aes(x = cut, fill = clarity)) +
            geom_bar(position = "stack")
ggplotly(p)
```

***

https://plot.ly/ggplot2/

If you use ggplot2, `ggplotly()` converts your plots to an interactive, web-based version! It also provides sensible tooltips, which assists decoding of values encoded as visual properties in the plot.

plotly supports some chart types that ggplot2 doesn't (such as 3D surface, point, and line plots). You can create these (or any other plotly) charts using `plot_ly()`.

